### 2015-12-31 paper-arxiv-v2/sec-mva.tex
Added v2 of paper in repo

At the end of the cut-based analysis,
by combining the three event topologies,
we obtain a signal significance of $S/\sqrt{B}\simeq 1.8~(3.5)$
with all backgrounds (only QCD $4b$) considered.
%
This section describes how this signal significance
 can be enhanced when the cut-based analysis
 is complemented by a multivariate analysis.
%
 Multivariate techniques are a mature tool
 in high-energy physics data analysis, opening
 new avenues to improve the performance
of many measurements and searches at high-energy colliders.
%
In particular, the classification of events into
signal and
background processes by means of MVAs is
commonly used in LHC
applications~\cite{Baldi:2014pta,Aaltonen:2012qt,
  Wardrope:2014kya,Chatrchyan:2013zna,Dall'Osso:2015aia}.

@@

%
The specific type of  MVA that we use to
disentangle signal and background events is
a multi-layer feed-forward artificial neural network (ANN),
known as a {\it perceptron}.\footnote{This type of ANNs are the same
  as those used to parametrize Parton Distribution Functions
in the NNPDF global analyses~\cite{DelDebbio:2004qj,Ball:2008by,Ball:2011mu,Ball:2010de}.}
%
This family of ANNs are also known as {\it deep neural networks},
due to their multi-layered architecture.
%
The MVA inputs are a set of kinematic variables describing the
signal and background
events which satisfy the requirements of the
cut-based analysis.
%
The output of the trained ANNs also allows for the identification,
in a fully automated way,
of the most relevant variables in the discrimination between 
signal and background.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
      \vspace{-1cm}
  \includegraphics[width=0.90\textwidth]{plots/bst_nnarch_noPU.pdf}
  \vspace{-2cm}
  \caption{\small Schematic of the Artificial
    Neural Network (ANN)
    used for the analysis of the
    boosted
    category, with $N_{\rm var}=21$ input variables and thus
    the same number of neurons
  in the first layer.
  %
  The color code in the neuron connections (the weights) is a heat map obtained
  at the end of the GA training,
  with red indicating larger values and black indicating smaller values.
}
\label{fig:nnarch}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

 \subsection{Input kinematical variables}
 \label{sec:input}

@@

Given that the MVA is able to identify the most discriminatory variables
in an automated way,
and to suppress those which have little effect, it is advantageous to
include a wide array of input variables.
%
This is one of the main advantages of ANNs in this context: 
their inherent redundancy means that 
adding additional information, even if carries very little weight,
should not degrade
the classification power of the MVA, aside from making the GA
minimization somewhat less efficient.

@@

We now present the results of the MVA, first without PU, and then
later including the effects of PU.
%
First of all, in Fig.~\ref{fig:nnresponse} we show the distribution of
the ANN output at the end of the GA minimization, for the exclusive
boosted, intermediate and resolved categories.
%
All distributions are normalized so that their integral
  adds up to one.
%
The  separation between signal and background is achieved by introducing
a cut, $y_{\rm cut}$, on the ANN output, so that MC events with $y_i\ge
y_{\rm cut}$ are classified as signal events, and those with
 $y_i <
y_{\rm cut}$ as background events.
%
Therefore,
the more differentiated the distribution of the ANN output is
for signal and background events, the more efficient
the MVA discrimination will be.

@@

From Fig.~\ref{fig:nnresponse} we see that in the boosted category the MVA can produce
a clear discrimination between signal and background, with the two distributions
forming peaks at their respective optimal limits.
%
This indicates that introducing a suitable cut
$y_{\rm cut}$
in the ANN output will substantially reduce the background,
while keeping a reasonable signal efficiency.
%
The performance of the MVA discrimination is similar, although slightly worse in the intermediate
and resolved categories.
%
The results for the signal selection efficiency and the 
background rejection rate as a function of the cut in the ANN output
$y_{\rm cut}$
define the so-called  Receiver-Operating Characteristic (ROC)
curve, shown in Fig.~\ref{fig:exampleroc}.
%
It is clear that we can achieve  high signal efficiency by using
a small value of $y_{\rm cut}$, but such a choice would be
affected by poor background
rejection.
%
Conversely, using a higher value of the cut will increase background rejection at the
cost of dropping signal efficiency.
%
As could already be inferred from the distribution of neural
networks output in Fig.~\ref{fig:nnresponse}, we find
that our MVA is reasonably efficient
in discriminating signal over background.
%
The performance is best in the case of the boosted category,
and then slightly worse in the resolved
and intermediate categories, consistent with the distributions of
the ANN outputs from
Fig.~\ref{fig:nnresponse}.
%

@@

It is important to verify for each value of
the cut in the ANN output $y_{\rm cut}$, how many
signal and background events are expected at the HL-LHC,
with an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$.
%
This comparison is shown in 
Fig.~\ref{fig:nev2}.
%
We observe that
in the boosted category, for a value $y_{\rm cut}\simeq 0.8$
we end up with 800 signal events and around $2\cdot 10^4$ background
events.
%
Similar results are obtained in the intermediate and resolved
categories: in the former we find 700 ($6\cdot 10^3$) signal (background)
events for $y_{\rm cut}\simeq 0.8$, and in the latter
1300 ($8\cdot 10^4$) signal (background) events for
$y_{\rm cut}\simeq 0.65$.
%
Note that the MVA achieves a very substantial background suppression
with only a
moderate reduction of signal efficiency.

A useful property of MVAs such as the one used in our
analysis,
is that they can provide direct  physical insight about which of the
input variables contribute the most to the separation between
signal and background.
%
In the case of ANNs, this can be quantified by computing the sum
of the absolute value of all the weights connected to a given
input neuron $i$, that is
\be
\label{eq:totweight}
\omega^{\rm (tot)}_i \equiv \sum_{k=1}^{n^{(2)}} \Big|\omega^{(2)}_{ki}\Big| \, ,
\qquad i=1,\ldots,N_{\rm var} \, ,
\ee
with $\omega^{(2)}_{ki}$ the value of the weight connecting
the $k$-th neutron of the second layer with the $i$-th neuron of
the first (input) layer, and $n^{(2)}=5$ the number of
neurons in the second layer.
%
Those input variables with a larger value of $\omega^{\rm (tot)}_i$ will be those
that play a more significant role in enhancing the signal
discrimination using the MVA.

@@

%
In Fig.~\ref{fig:nnweights} we show
the distribution of the total associated weight,
Eq.~(\ref{eq:totweight}) for each of the $N_{\rm var}$ input
variables of the three categories, using the
notation for the various kinematic variables
as in Sect.~\ref{sec:input}.
%
% The important information
% is contained in the relative strengths of the total associated weight
% for each of the input variables.
%
In the 
resolved category, the variables that carry 
a higher discrimination power
are the $p_T$ of the two reconstructed Higgs candidates and
their invariant masses $m_{h1}$ and $m_{h2}$.
%
In the case of the boosted category, the invariant mass distribution
of the Higgs candidates is also the most discriminatory
variable, followed by the subjet $p_T$ distributions and
substructure variables such as $C_2^{(\beta)}$ and
$D_2^{(\beta)}$.

@@

The results for the signal significance $S/\sqrt{B}$ and
the signal over background ratio
$S/B$ as a function of $y_{\rm cut}$
for the three categories are given in 
Fig.~\ref{fig:sb_mva}.
%
The values 
for $y_{\rm cut}=0$ correspond to those at
the end of the cut-based analysis.
%
We observe how in the three
 categories there is a marked  improvement in signal
significance as compared to the pre-MVA results.
%
We also observe a substantial enhancement in $S/B$, arising
from the background suppression achieved by the MVA, reaching
values of 1\%, 6\% and 3.5\% in the resolved,
intermediate and boosted categories.
%
This improvement in $S/B$ is crucial to ensure the feasibility
of this measurement, since it allows systematic
uncertainties in the background determination to
be at the same level of a few percent.

We now have all the
information needed to determine a suitable
value of the MVA output cut $y_{\rm cut}$ in each
of the three categories.
%
These values can be determined from the maximisation of $S/\sqrt{B}$,
ensuring that the number of signal events $N_{\rm ev}$
expected at the HL-LHC does not become too low.
%
In  addition we require
that the number of MC events used to define the signal
category (events with $y_i \ge y_{\rm cut}$)
is sufficiently large in order to avoid the biases and statistical
fluctuations associated to a small training sample.
%
In Table~\ref{table:cutflowMVA} we quote
the value of the optimal ANN output
cut in each category,
the number of signal and background events $N_{\rm ev}$ expected
at the HL-LHC as well as $S/\sqrt{B}$ and $S/B$.
%
For reference, we also include the results at the end of
the cut-based
analysis.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|l|c|c|c|c|}
    \hline
    \multicolumn{6}{|c|}{No PU} \\
    \hline
    \hline
    Category  &   &  $N_{\rm ev}$ signal &  $N_{\rm ev}$ back  &  $S/\sqrt{B}$ & $S/B$ \\ 
    \hline
    \hline
    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 1070 & $7.6\cdot 10^5$  & 1.2  & $1.4\cdot 10^{-3}$  \\
    &  $y_{\rm cut}=0.82$ & 790  & $2.2\cdot 10^4$   & 5.4  & 0.03 \\
    \hline
    \hline
    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  & 670   & $5.3\cdot 10^5$
    & 0.9 & $1.2\cdot 10^{-3}$ \\
    &  $y_{\rm cut}=0.80$ & 360  & $5.5\cdot 10^3$  & 4.8 & 0.06\\
    \hline
    \hline
      \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  & 3700 &  $1.5\cdot 10^{7}$ &  1.0 &$3\cdot 10^{-4}$ \\
    &  $y_{\rm cut}=0.65$ & 1300  & $8.3\cdot 10^{4}$ & 4.5 & 0.01 \\
    \hline
      \end{tabular}
  \caption{\small Post-MVA results, for the optimal value of the
    ANN discriminant $y_{\rm cut}$ in the three categories, compared with the
    corresponding
    pre-MVA results $y_{\rm cut}=0$.
    %
    We quote the number of signal and
    background events
    at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$,
    the signal significance $S/\sqrt{B}$ and
    the signal over background ratio $S/B$.
    %
    The pre-MVA results ($y_{\rm cut}=0$) corresponds to row C2 in
    Table~\ref{tab:cutflow_noPU_1}.
    \label{table:cutflowMVA}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

From Table~\ref{table:cutflowMVA} we see that
after the application of the MVA, 
the signal significance in the boosted category increases
from 1.2 to 5.4, with $S/B$ increasing from $0.14\%$ to $3.4\%$,
with almost 800 signal events expected at the HL-LHC.
%
For the intermediate and resolved categories, $S/\sqrt{B}$
increases from 0.9 and 1.0 to 4.8 and 4.5, with
the signal over background ratio raising from
$0.12\%$ and $0.03\%$ to 6\% and 1\%, respectively.
%
The overall combined significance is thus $S\sqrt{B}\simeq 8$,
well above the threshold for discovery.
%
However, given that the HL-LHC will be a high-PU environment,
which will affect the description of the various
kinematical distributions used as input to the MVA,
it is essential to quantify the robustness of these
results
in a realistic environment including the effects of PU.

@@

In this section we study how the MVA results are modified
when the analysis is performed including significant PU.
%
The cut-based analysis and the subsequent
MVA optimization have been performed using the same
settings as in the case without PU.
%
In Table~\ref{tab:cutflow_PU80_1}
we provide the pre-MVA cut flow in the case of PU,
the corresponding version without PU is
Table~\ref{tab:cutflow_noPU_1}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \scriptsize
      \input{table_PU80.tex}
    \caption{\small Same as Table~\ref{tab:cutflow_noPU_1}
for the case  now for the case
    of PU+SK+Trim with $\la n_{\rm PU}\ra=80$.
 \label{tab:cutflow_PU80_1}}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Table~\ref{table:cutflowMVA_PU} we provide the results
  at the end of the cut-based analysis,
  for the case with $\la n_{\rm PU}\ra=80$ with SK+Trim
  subtraction,
  as well as the post-MVA results for the
  corresponding optimal values of $y_{\rm cut}$.
  %
  Additionally we quote in
  both cases the number of signal and
    total background events expected
    at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$
    and the values of $S/\sqrt{B}$ and $S/B$

We observe that the pre-MVA 
signal significance is close
to the case without PU for the three categories.
%
We now find values for $S/\sqrt{B}$ of 0.9, 0.7 and 1.5, in the resolved,
intermediate and boosted categories, respectively, to be compared
with the corresponding values without PU, namely 1.0, 0.9 and 1.0.
%
The number of selected
signal events in each category, at the
end of the cut-based analysis, is only mildly affected
by PU.
%
The slight pre-MVA improvement in $S/\sqrt{B}$ for the
boosted case arises from a reduction in the number
of background events that are classified in this category
as compared to the case without PU.

Once the MVA is applied, the signal significance in the 
resolved, intermediate and boosted
categories increases to 4.6, 4.1 and 3.7 respectively,
to be compared with the corresponding values
without PU, namely 4.5, 4.8 and 5.4.
%
Therefore, the post-MVA effect of PU on $S/\sqrt{B}$ is
a moderate degradation of the boosted and intermediate categories,
while the resolved category is largely unchanged.
%
We also observe that, due
to the MVA, the
signal over background ratio is increased from 0.02\%, 0.08\% and
0.2\% up to 1\%, 4\% and 2\% in the resolved, intermediate
and boosted categories respectively.
%
This indicates that while this measurement is still highly challenging,
requiring a careful extraction of the QCD
background from the data, it is certainly within reach.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|l|c|c|c|c|}
        \hline
     \multicolumn{6}{|c|}{$\la n_{\rm PU}\ra=80$+SK+Trim} \\
     \hline
         \hline
    Category  &   &  $N_{\rm ev}$ signal &  $N_{\rm ev}$ back  &  $S/\sqrt{B}$ & $S/B$ \\ 
    \hline
    \hline
    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 1000   &  $4.5\cdot 10^5$ & 1.5   & $2\cdot 10^{-3}$  \\
    &  $y_{\rm cut}=0.7$ &  780  & $4.5\cdot 10^4$  & 3.7    & 0.02  \\
    \hline
    \hline
    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  &  630  & $8.2\cdot 10^5$    & 0.7    &
     $8\cdot 10^{-4}$ \\
    &  $y_{\rm cut}=0.7$ & 380 & $8.5\cdot 10^3$  &  4.1   & 0.04 \\
    \hline
    \hline
    \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &  4500  & $2.7\cdot 10^7$
    & 0.9    &  $2\cdot 10^{-4}$  \\
    &  $y_{\rm cut}=0.5$ & 2000  & $2.1\cdot 10^5$  &  4.6   & 0.01  \\
    \hline
      \end{tabular}
  \caption{\small Same as Table~\ref{table:cutflowMVA}, now for the case
    of PU+SK+Trim, with $\la n_{\rm PU}\ra=80$.
        \label{table:cutflowMVA_PU}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.49\textwidth]{plots/roc_SKPU80.pdf}
\includegraphics[width=0.49\textwidth]{plots/nev2_SKPU80.pdf}
\caption{\small Same as Fig.~\ref{fig:nev2} in the
case of events with PU, for
$\la n_{\rm PU}\ra=80$ with SK+Trim.
}
\label{fig:nev2_PU}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

At the end of the loose cut-based analysis,
by combining the three event topologies,
we obtain a signal significance of $S/\sqrt{B}\simeq 0.8~(1.4)$
with all backgrounds (only QCD $4b$) considered.
%
This section describes how this signal significance
 can be enhanced when the cut-based analysis
 is complemented by multivariate techniques.
%
 These are by now a mature tool
 in high-energy physics data analysis, opening
 new avenues to improve the performance
of many measurements and searches at high-energy colliders.
%
In particular, the classification of events into
signal and
background processes by means of MVAs is
commonly used in LHC
applications~\cite{Baldi:2014pta,Aaltonen:2012qt,
  Wardrope:2014kya,Chatrchyan:2013zna,Dall'Osso:2015aia}.

@@

The specific type of  MVA that we use to
disentangle signal and background events is
a multi-layer feed-forward artificial neural network (ANN),
known as a {\it perceptron}.\footnote{This type of ANNs are the same
  as those used to parametrize Parton Distribution Functions
in the NNPDF global analyses~\cite{DelDebbio:2004qj,Ball:2008by,Ball:2011mu,Ball:2010de}.}
%
This family of ANNs are also known as {\it deep neural networks},
due to their multi-layered architecture.
%
The MVA inputs are a set of kinematic variables describing the
signal and background
events which satisfy the requirements of the
cut-based analysis.
%
The output of the trained ANNs also allows for the identification,
in a fully automated way,
of the most relevant variables in the discrimination between 
signal and background.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
      \vspace{-1cm}
  \includegraphics[width=0.90\textwidth]{plots/bst_nnarch_noPU.pdf}
  \vspace{-2cm}
  \caption{\small Schematic of the Artificial
    Neural Network (ANN)
    used for the analysis of the
    boosted
    category, with $N_{\rm var}=21$ input variables and thus
    the same number of neurons
  in the first layer.
  %
  The color code in the neuron connections (the weights) is a heat map obtained
  at the end of the Genetic Algorithms training,
  with red indicating larger values and black indicating smaller values.
}
\label{fig:nnarch}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

 \subsection{Input kinematic variables}
 \label{sec:input}

@@

Given that the MVA is able to identify the most discriminatory variables
in an automated way,
and to suppress those which have little effect, it is advantageous to
include a wide array of input variables.
%
This is one of the main advantages of ANNs in this context: 
their inherent redundancy means that 
adding additional information, even if carries very little weight,
should not degrade
the classification power of the MVA.

@@

We now present the results of the MVA, first without PU, and then
later including the effects of PU.
%
First of all, in Fig.~\ref{fig:nnresponse} we show the distribution of
the ANN output at the end of the GA minimization,
separately for the
boosted, intermediate and resolved categories.
%
All distributions are normalized so that their integral
  adds up to one.
%
The  separation between signal and background is achieved by introducing
a cut, $y_{\rm cut}$, on the ANN output, so that MC events with $y_i\ge
y_{\rm cut}$ are classified as signal events, and those with
 $y_i <
y_{\rm cut}$ as background events.
%
Therefore,
the more differentiated the distribution of the ANN output is
for signal and background events, the more efficient
the MVA discrimination will be.

@@

From Fig.~\ref{fig:nnresponse} we see that in the boosted category the MVA can produce
a clear discrimination between signal and background, with the two distributions
forming peaks at their respective optimal limits.
%
This indicates that introducing a suitable cut
$y_{\rm cut}$
in the ANN output will substantially reduce the background,
while keeping a reasonable signal efficiency.
%
The performance of the MVA discrimination is similar,
although slightly worse, in the intermediate
and resolved categories.

The results for the signal selection efficiency and the 
background rejection rate as a function of the cut in the ANN output
$y_{\rm cut}$
define the so-called  Receiver-Operating Characteristic (ROC)
curve, shown in Fig.~\ref{fig:exampleroc}.
%
It is clear that we can achieve  high signal efficiency by using
a small value of $y_{\rm cut}$, but such a choice would be
affected by poor background
rejection.
%
Conversely, using a higher value of the cut will increase background rejection at the
cost of dropping signal efficiency.
%
As could already be inferred from the distribution of neural
networks output in Fig.~\ref{fig:nnresponse}, we find
that our MVA is reasonably efficient
in discriminating signal over background.
%
The performance is best in the case of the boosted category,
and then slightly worse in the resolved
and intermediate categories, consistent with the distributions of
the ANN outputs in
Fig.~\ref{fig:nnresponse}.
%

@@

It is useful to estimate, for each value of
the cut in the ANN output $y_{\rm cut}$, how many
signal and background events are expected at the HL-LHC
with $\mathcal{L}=3$ ab$^{-1}$.
%
This comparison is shown in 
Fig.~\ref{fig:nev2}.
%
We observe that
in the boosted category, for a value $y_{\rm cut}\simeq 0.9$
we end up with around 300 signal events and $10^4$ background
events.
%
Similar results are obtained in the intermediate and resolved
categories: in the former we find 130 ($3\cdot 10^3$) signal (background)
events for $y_{\rm cut}\simeq 0.85$ (0.60), and in the latter
630 ($10^5$) signal (background) events for
$y_{\rm cut}\simeq 0.6$.
%
Therefore, the MVA achieves a
substantial background suppression
with only a
moderate reduction of signal efficiency.

A useful property of MVAs such as the one used in our
analysis
is that they can provide direct  physical insight about which of the
input variables contribute to the separation between
signal and background.
%
In the case of ANNs, this can be quantified by computing the sum
of the absolute values of all the weights connected to a given
input neuron $i$, that is
\be
\label{eq:totweight}
\omega^{\rm (tot)}_i \equiv \sum_{k=1}^{n^{(2)}} \Big|\omega^{(2)}_{ki}\Big| \, ,
\qquad i=1,\ldots,N_{\rm var} \, ,
\ee
with $\omega^{(2)}_{ki}$ the value of the weight connecting
the $k$-th neutron of the second layer with the $i$-th neuron of
the first (input) layer, and $n^{(2)}=5$ the number of
neurons in the second layer.
%
Those input variables with a larger value of $\omega^{\rm (tot)}_i$ will be those
that play a more significant role in enhancing the signal
discrimination using the MVA.
%
We note however
that the estimate provided
by Eq.~(\ref{eq:totweight}) is necessarily qualitative.

@@

%
In Fig.~\ref{fig:nnweights} we show
the distribution of the total associated weight,
Eq.~(\ref{eq:totweight}) for each of the $N_{\rm var}$ input
variables of the three categories, using the
notation for the kinematic variables
as in Sect.~\ref{sec:input}.
%
In the 
resolved category, the variables that carry 
a higher discrimination power
are the transverse momentum of the two reconstructed Higgs candidates and
their invariant masses.
%
In the case of the boosted category, the invariant mass distribution
of the Higgs candidates is also the most discriminatory
variable, followed by the subjet $p_T$ distributions and
substructure variables such as $C_2^{(\beta)}$ and
$D_2^{(\beta)}$.

@@

The results for the signal significance $S/\sqrt{B}$ and
the signal over background ratio
$S/B$ as a function of $y_{\rm cut}$
for the three categories are given in 
Fig.~\ref{fig:sb_mva}.
%
The values 
for $y_{\rm cut}=0$ correspond to those at
the end of the loose cut-based analysis.
%
We observe how in the three
 categories there is a marked  improvement in signal
significance as compared to the pre-MVA results.
%
We also observe a substantial enhancement in $S/B$, arising
from the background suppression achieved by the MVA, reaching
values of 1\%, 6\% and 3.5\% in the resolved,
intermediate and boosted categories.
%
This improvement in $S/B$ is crucial to ensure the feasibility
of this measurement, since it allows systematic
uncertainties in the background determination to
be at most of a similar size.

%
The optimal value of the cut in the
ANN output, $y_{\rm cut}$,  can be determined from the maximisation of $S/\sqrt{B}$,
ensuring that the number of signal events $N_{\rm ev}$
expected at the HL-LHC does not become too low.
%
In  addition, we require
that the number of MC events used to define the signal
category (events with $y_i \ge y_{\rm cut}$)
is sufficiently large in order to avoid the biases and statistical
fluctuations associated to a small training sample.
%
In Table~\ref{table:cutflowMVA} we quote, for the optimal
value of $y_{\rm cut}$
in each category,
the number of signal and background events $N_{\rm ev}$ expected
at the HL-LHC, as well as $S/\sqrt{B}$ and $S/B$.
%
For completeness, we also include the corresponding
pre-MVA results.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|l|c|c|c|c|}
    \hline
    \multicolumn{6}{|c|}{HL-LHC, no PU} \\
    \hline
    \hline
    Category  &   &  $N_{\rm ev}$ signal &  $N_{\rm ev}$ back  &  $S/\sqrt{B}$ & $S/B$ \\ 
    \hline
    \hline
    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 440 & $7.6\cdot 10^5$  & 0.5  & $6\cdot 10^{-4}$  \\
    &  $y_{\rm cut}=0.90$ & 290  & $1.2\cdot 10^4$   & 2.7  & 0.03 \\
    \hline
    \hline
    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  & 280   & $5.3\cdot 10^5$
    & 0.4 & $5\cdot 10^{-4}$ \\
    &  $y_{\rm cut}=0.85$ & 130  & $3.1\cdot 10^3$  & 2.3 & 0.04\\
    \hline
    \hline
      \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  & 1500 &  $1.5\cdot 10^{7}$ &  0.4 &$1\cdot 10^{-4}$ \\
    &  $y_{\rm cut}=0.60$ & 630  & $1.1\cdot 10^{5}$ & 1.9 & 0.01 \\
    \hline
      \end{tabular}
  \caption{\small Post-MVA results, for the optimal value of the
    ANN discriminant $y_{\rm cut}$ in the three categories, compared with the
    corresponding
    pre-MVA results ($y_{\rm cut}=0$).
    %
    We quote the number of signal and
    background events expected for $\mathcal{L}=3$ ab$^{-1}$,
    the signal significance $S/\sqrt{B}$ and
    the signal over background ratio $S/B$.
    %
    The pre-MVA results correspond to row C2 in
    Table~\ref{tab:cutflow_noPU_1}.
    \label{table:cutflowMVA}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

From Table~\ref{table:cutflowMVA} we see that
following the application of the MVA, 
the signal significance in the boosted category increases
from 0.5 to 2.7, with $S/B$ increasing from $0.06\%$ to $3\%$.
%
For the intermediate and resolved categories, $S/\sqrt{B}$
increases from 0.4 to 2.3 and 1.9 respectively, with
the signal over background ratio raising from
$0.05\%$ and $0.01\%$ to 4\% and 1\%.
%
Combining the three categories, taking into
account all background components, we obtain the overall signal
significance:
\be
\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0~(1.3) \, ,\quad
\mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, ,
\ee
%
The signal significance for
$\mathcal{L}=3$ ab$^{-1}$
is thus
well above the threshold for the observation of Higgs
pair production.
%
However, given that the HL-LHC will be a high-PU environment,
which will affect the description of the various
kinematic distributions used as input to the MVA,
it is essential to quantify the robustness of these
results
in a realistic environment including the effects of
significant PU.

@@

In this section we study how the MVA results are modified
when the analysis is performed including significant PU.
%
The loose cut-based analysis and the subsequent
MVA optimization have been performed using the same
settings as in the case without PU.
%
In Table~\ref{tab:cutflow_PU80_1}
we provide the pre-MVA cut flow in the case of PU80,
the corresponding version without PU being
Table~\ref{tab:cutflow_noPU_1}.
%
The interplay between the signal cross-sections and the various
background components is qualitatively unchanged as compared
to the no PU case.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \scriptsize
      \input{table_PU80.tex}
    \caption{\small Same as Table~\ref{tab:cutflow_noPU_1},
now for the case
    of PU80+SK+Trim.
 \label{tab:cutflow_PU80_1}}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Table~\ref{table:cutflowMVA_PU} we compare the results
for the PU80+SK+Trim case between
  the pre-MVA loose cut-based analysis and
  the post-MVA results for the
  optimal values of the ANN output cut $y_{\rm cut}$.
  %
  As in Table~\ref{table:cutflowMVA}, 
  we also quote 
   the number of signal and
    total background events expected
   for $\mathcal{L}=3$ ab$^{-1}$
    and the values of $S/\sqrt{B}$ and $S/B$.
%
We observe that the pre-MVA 
signal significance is close
to the results of the simulations
without PU for the three categories.
%
We now find values for $S/\sqrt{B}$ of 0.4, 0.3 and 0.6, in the resolved,
intermediate and boosted categories, respectively, to be compared
with the corresponding values without PU, namely 0.4, 0.4 and 0.5.
%
The number of selected
signal events in each category at the
end of the cut-based analysis is only mildly affected
by PU.
%
The slight pre-MVA improvement in $S/\sqrt{B}$ for the
boosted case arises from a reduction in the number
of background events that are classified in this category
as compared to the case without PU.

Once the MVA is applied, the signal significance in the 
resolved, intermediate and boosted
categories increases to 2.0, 1.9 and 1.5 respectively,
to be compared with the corresponding values
without PU, namely 1.9, 2.3 and 2.7.
%
Therefore, the post-MVA effect of PU on $S/\sqrt{B}$ is
a moderate degradation of the boosted and intermediate categories,
specially for the former,
while the resolved category is largely unchanged.\footnote{
  The impact of PU on the  separate significance of
  the three categories exhibits some
  dependence on the specific choice for $n_{\rm PU}$  and on the settings
  of the PU subtraction strategy.
  %
  We find however that the
  overall signal significance from combining the three
  categories is similar in the $n_{\rm PU}=80$ and
  $n_{\rm PU}=150$ cases.
}
%
We also observe that, due
to the MVA, the
signal over background ratio is increased from 0.007\%, 0.03\% and
0.1\% up to 1\%, 3\% and 1\% in the resolved, intermediate
and boosted categories respectively.
%
This indicates that while this measurement is still highly challenging,
requiring a careful extraction of the QCD
background from the data, it should be within reach.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|l|c|c|c|c|}
        \hline
     \multicolumn{6}{|c|}{HL-LHC, PU80+SK+Trim} \\
     \hline
         \hline
    Category  &   &  $N_{\rm ev}$ signal &  $N_{\rm ev}$ back  &  $S/\sqrt{B}$ & $S/B$ \\ 
    \hline
    \hline
    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 410   &  $4.5\cdot 10^5$ & 0.6   & $ 10^{-3}$  \\
    &  $y_{\rm cut}=0.8$ &  290  & $3.7\cdot 10^4$  & 1.5    & 0.01  \\
    \hline
    \hline
    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  &  260  & $7.7\cdot 10^5$    & 0.3    &
     $3\cdot 10^{-4}$ \\
    &  $y_{\rm cut}=0.75$ & 140 & $5.6\cdot 10^3$  &  1.9   & 0.03 \\
    \hline
    \hline
    \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &  1800  & $2.7\cdot 10^7$
    & 0.4    &  $7\cdot 10^{-5}$  \\
    &  $y_{\rm cut}=0.60$ & 640  & $1.0\cdot 10^5$  &  2.0   & 0.01  \\
    \hline
      \end{tabular}
  \caption{\small Same as Table~\ref{table:cutflowMVA}, now for the case
    of PU80+SK+Trim.
        \label{table:cutflowMVA_PU}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.49\textwidth]{plots/roc_SKPU80.pdf}
\includegraphics[width=0.49\textwidth]{plots/nev2_SKPU80.pdf}
\caption{\small Same as Fig.~\ref{fig:nev2}
 for
 the PU80+SK+Trim case.
\label{fig:nev2_PU}}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
